Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-08 gibbs.tex
Apply 1 suggestion(s) to 1 file(s)

By the \emph{open system} we mean that the gel is equlibrated with an \textbf{infinite} reservoir outside, such that there are the same ions chemical potential, the same temperature and desired pressure difference between the gel and the reservoir. Number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.

>>>>

By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with an \textbf{infinite} reservoir of an aqueous solution.
%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
